What do incoming university students believe about open science practices in

### 2022-04-09 analysis/Manuscript.Rmd
add text re twitter thread

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, SA, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
 Objective: We examined what incoming undergraduate students of psychology believe about reproducibility and open science practices.
 Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked to indicate how a researcher should conduct her study, most students endorsed several open science practices. When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates averaged near 50%. Only 18% of participants reported that they had heard the term "replication crisis".
 Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless in favour of most open science practices, although they overestimated the prevalence of some of these practices in psychology.
 Teaching Implications: Teachers of incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: 3009
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

# convert variables to factors as needed
df$age <- as_factor(df$age)
df$eligibility <- as_factor(df$eligibility)

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. These contacts were identified via several avenues: a session at the annual meeting of the Society for the Improvement of Psychological Science (2019), a Twitter thread, and through contacts of the research team. We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, SA, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
 Objective: We examined what incoming undergraduate students of psychology believe about reproducibility and open science practices.
 Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked to indicate how a researcher should conduct her study, most students endorsed several open science practices. When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates averaged near 50%. Only 18% of participants reported that they had heard the term "replication crisis".
 Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless in favour of most open science practices, although they overestimated the prevalence of some of these practices in psychology.
 Teaching Implications: Teachers of incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: 3011
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

# convert variables to factors as needed
df$age <- as_factor(wtdf$age)
df$eligibility <- as_factor(df$eligibility)

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. These contacts were identified through several avenues: direct contact with our colleagues, a session at the international meeting of the Society for the Improvement of Psychological Science (2019), and a Twitter thread with >15,000 impressions. We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
